prep_annotating

### 2022-06-21 code/prep_annotate.Rmd
sample graphs from 1 annotated game

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=F, warning=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))

@@

```
See https://docs.google.com/presentation/d/1qcDRZzHbLhE-fp6W9nKcbGouj4w01qCLCy-yt072iiY/edit?usp=sharing (purple flowers) for the flower number - image correspondence.

sample %>% filter(!is.na(span)) %>% select(trialNum, name, referent, span) %>% arrange(referent) %>% knitr::kable(align="l")
```
